---
title: "SST data for July 2019 new"
author: "LRA"
date: "1/24/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
Region_order <- c("AK","BC","WA","OR","BB","SD")
SiteCode_order <- c("A","B","C","D","E","F")
```

```{r data, echo=FALSE}
site_temps <- read.csv("Sat_Temps_July_2019.csv")
site_temps$Region <- ordered(site_temps$Region,levels=Region_order)
site_temps$SiteCode <- ordered(site_temps$SiteCode,levels=SiteCode_order)
site_temps$time <- as.POSIXct(site_temps$time,tz="")
```

Here, I am using data temperature data from NOAA's 5km Geo-Polar Blended Night-time SST

Data were downloaded from the PacIOOS's ERDDAP server (https://pae-paha.pacioos.hawaii.edu/erddap/griddap/dhw_5km.html)

Two variables of interest: SST and SST Anomaly, which is the difference in the SST compared to the long-term record.

Plots show the distributions of SST and SST Anomaly at 19 of the 32 NSF sites surveyed for SWD in July 2019.

At the remainig 13 sites, the satellite data are not available for the closest pixel


```{r julySST, echo=FALSE}
ggplot(site_temps,aes(x=time,y=CRW_SST,color=SiteCode))+geom_point()+
  facet_wrap(~Region)+
  xlab("Date")+
  ylab("Nighttime SST measured via satellite (ºC)")+
  labs(title="SST during July 2019 across NSF sites",
       subtitle="5-km resolution")+
  theme_bw()+
  theme(strip.background = element_rect(fill="white"))

ggplot(site_temps,aes(x=SiteCode,y=CRW_SST))+geom_boxplot()+
  stat_summary(fun.y=mean,geom="point",shape=8,size=2)+
  facet_wrap(~Region)+
  xlab("Site Code")+
  ylab("SST (ºC)")+
  labs(title = "SST in July 2019 from satellite data",
       subtitle = "5-km resolution")+
  theme_bw()+
  theme(strip.background = element_rect(fill="white"))
```

```{r julySSTANOMALY, echo=FALSE}
ggplot(site_temps,aes(x=SiteCode,y=CRW_SSTANOMALY))+geom_boxplot()+
  stat_summary(fun.y=mean,geom="point",shape=8,size=2)+
  facet_wrap(~Region)+
  xlab("Site Code")+
  ylab("SST Anomaly (ºC)")+
  labs(title = "SST Anomaly in July 2019 from satellite data",
       subtitle = "5-km resolution")+
  theme_bw()+
  theme(strip.background = element_rect(fill="white"))

```

