---
title: "SST data for July 2019"
author: "LRA"
date: "1/22/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

```{r data, include=FALSE}
## read-in data from NOAA Coastal Reef Watch, for full range of NSF sites during July 2019
temps <- read.csv("dhw_5km_8211_97f8_5ea5.csv",header=TRUE)[-1,]
## Subset dataset to look at only the SST and SSTANOMALY (difference compared to long-term mean)
temps2 <- temps[,c(1,2,3,7,8)]
## The variables are read in as factors - convert to numeric, then character and drop empty rows
temps2$CRW_SST <- as.character(temps2$CRW_SST)
temps2$CRW_SST <- as.numeric(temps2$CRW_SST)
temps2 <- na.omit(temps2)

temps2$CRW_SSTANOMALY <- as.character(temps2$CRW_SSTANOMALY)
temps2$CRW_SSTANOMALY <- as.numeric(temps2$CRW_SSTANOMALY)
temps2$latitude <- as.character(temps2$latitude)
temps2$latitude <- as.numeric(temps2$latitude)
temps2$longitude <- as.character(temps2$longitude)
temps2$longitude <- as.numeric(temps2$longitude)

## Convert times to POSIXct class in order to treat as dates (should be automatic)
temps2$time <- as.character(temps2$time)
temps2$time <- as.POSIXct(temps2$time,tz="")

#Subset for WA region using bounding lat and long 
WA <- temps2[temps2$latitude<48.775 & temps2$latitude>48.42501 & temps2$longitude>-123.225 & temps2$longitude< -122.725,]
# Use site coordinates to identify the correct pixels to match each site code
# Note the site E coordinates were not working for some reason so used the surrounding pixels to identify 
WA$SiteCode <- ifelse(WA$latitude==48.47500 & WA$longitude== -122.975,"A",
                      ifelse(WA$latitude==48.47500 & WA$longitude== -123.075, "B",
                             ifelse(WA$latitude==48.67501 & WA$longitude== -122.975, "C",
                                    ifelse(WA$latitude==48.72500 & WA$longitude== -123.075, "D",
                                           ifelse(WA$latitude<48.62501 & WA$latitude>48.52500
                                                  & WA$longitude< -122.875 & WA$longitude> -123.025, "E","NA")))))
WA.sites <- subset(WA,SiteCode!="NA")
```

Here, I am using data temperature data from NOAA's 5km Geo-Polar Blended Night-time SST

Data were downloaded from the PacIOOS's ERDDAP server (https://pae-paha.pacioos.hawaii.edu/erddap/griddap/dhw_5km.html)

Two variables of interest: SST and SST Anomaly, which is the difference in the SST compared to the long-term record.

Plots show the distributions of SST and SST Anomaly at the five sites in WA surveyed for SWD in July 2019.


```{r SST, echo=FALSE}
ggplot(WA.sites,aes(x=SiteCode,y=CRW_SST))+geom_boxplot()+
  stat_summary(fun.y=mean,geom="point",shape=8,size=2)+
  xlab("Site Code")+
  ylab("SST (ºC)")+
  labs(title = "SST in July 2019 at Washington Sites",
       subtitle = "5-km resolution")+
  theme_bw()
```

```{r SST_Anomaly, echo=FALSE}
ggplot(WA.sites,aes(x=SiteCode,y=CRW_SSTANOMALY))+geom_boxplot()+
  stat_summary(fun.y=mean,geom="point",shape=8,size=2)+
  xlab("Site Code")+
  ylab("SST Anomaly (ºC)")+
  labs(title = "SST Anomaly in July 2019 at Washington Sites",
       subtitle = "5-km resolution")+
  theme_bw()
```

There's somewhat of a N-S gradient, with furthest north sites C and D (Beach Haven and North Cove) having the warmest temps and greatest positive anomlies, and furthest south sites A and B (Fourth of July and False Bay) having the coolest temps and lowest anomalies. Beach Haven and North Cove also had the highest disease levels in 2019, so it will be interesting to see if this pattern holds up at other sites.

